modelling

### 2019-03-21 modelling.Rmd
rearranged model framework

### Model framework
An identical model specification is used across the six elections, with each election modelled separately. This allows for the socio-demographic effects to be estimated separately for each year, allowing for interpretation of temporal changes in these effects. This is preferable over a single longitudinal model because it avoids any concerns of undue bias stemming from an incorrectly imposed time-varying restriction on any variable. Without such restrictions, a pooled cross-sectional model does not yield any distinct advantage over separate models. The panel approach is avoided because of how frequently electoral boundaries change, so any fixed or random effects models would be inappropriate.

The response, the two-party preferred vote in favour of the Liberal party (denoted $Y$), lies in the interval $(0,100)$, where $Y = 70$ would represent a 70% preference for Liberal, 30% for Labor. Since the observed values of $Y$ are never very close to 0 or 100 (minimum $24.05 \%$ and maximum $74.90 \%$), there is no need to impose the constraint of $Y \in [0,100]$. Electorates represent aggregate spatial units, and a Moran's I test of the two-party preferred vote finds significant spatial autocorrelation for each election ($p \le 7\cdot10^{-15}$), so the spatial structure of the data must be taken into account. The spatial error model [@Anselin99] is chosen because it allows for spatial correlation in the errors. This can be thought of as capturing the political climate, where political pressures (unobserved characteristics influencing voter behaviour) of neighbours influence an electorate's voting behaviour. Spatial weights are calculated by allowing each electorate to be equally correlated with any electorate that shares any part of its boundary. The spatial error model is specified as follows:

@@

>>>>

### Model framework
An identical model specification is used across the six elections, with each election modelled separately. This allows for the socio-demographic effects to be estimated separately for each year, allowing for interpretation of temporal changes in these effects. This is preferable over a single longitudinal model because it avoids any concerns of undue bias stemming from an incorrectly imposed time-varying restriction on any variable. Without such restrictions, a pooled cross-sectional model does not yield any distinct advantage over separate models. The panel approach is avoided because of how frequently electoral boundaries change - electorates that have the same name across elections are not guaranteed to represent the same geographical region - meaning any fixed or random effects models would be difficult without implementing consistent boundaries requiring further imputation.

For each cross-section, let the response variable be the two-party preferred vote in favour of the Liberal party, denoted $Y$, with $Y = 70$ representing a 70% preference for Liberal, 30% for Labor. Although $Y$ lies in the interval $(0,100)$, observed values are never very close to 0 or 100 (minimum $24.05 \%$ and maximum $74.90 \%$), so there is no need to impose the constraint of $Y \in [0,100]$. Furthermore, the response is found to be spatially correlated in each election (Moran's I test, $p \le 7\cdot10^{-15}$). This is expected, as electorates are aggregate spatial units, and hence the spatial structure of the data must modelled appropriately.

The spatial error model [@Anselin99] is chosen because it allows for spatial correlation in the errors. This can be thought of as capturing the political climate, where political pressures (unobserved characteristics influencing voter behaviour) of neighbours influence an electorate's voting behaviour. Spatial weights are calculated by allowing each electorate to be equally correlated with any electorate that shares any part of its boundary. The spatial error model is specified as follows:

@@

----------------------------------------------------------------------------------------
